### 2013-08-01 Tex/chapters/results.tex
Tc Werte mit ausgewiesen
Tabelle der Tc eingefügt

\subsection{Finite Size Effects}
\label{ssec:finitesize}
    The aim of this thesis is to find the critical temperature \(T_c\)
    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
    the system will show a steep decline to zero and the susceptibility
    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
    it is easy to see that the steep decline of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\) (here with a RNG).
    \begin{figure}[htbp]
        \centering
        \subfigure[Dependence of the Phase Transition on $\sigma$][]
        {
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        }
        \subfigure[Example for Finite Size Effects][]
        {
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        }
        \caption[Phase Transition and Finite Size Effects]
        {
            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying RNG with $L=128$.\\
            \subref{sfig:smeared_out:meanM}: Effects of different system
            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
        }
        \label{fig:smeared_out}
    \end{figure}\\
    But in the shown plots there occurs no steep decline to zero, but a
    smooth decline. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
    systems, hence no computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finte size effects}.
    These finite size effects cause a "smearing out" of the phase
    transition. This is stronger for smaller system sizes, as is visible
    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999}, which also yield the critical
    exponents. This will be performed in the next section.
    Though there is an easier approach, which yields even more
    precise values for \(T_{c}\), which is presented in \ref{ssec:binderIntersections}.

@@

@@

    and the error of \(\nu\) is the standard deviation of the three obtained
    values of \(\nu\).\\

@@

        \begin{tabular}{l l l l l}

@@

             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\

@@

            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\

@@

            GG           & 0.0 & 0.998(8) & 1.735(2) & 0.1262(4)\\
                         & 0.1 & 0.999(19)& 1.744(5) & 0.133(6) \\
                         & 0.3 & 1.029(30)& 1.724(16)& 0.129(12)\\
                         & 0.5 & 1.006(5) & 1.750(12)& 0.125(13)\\
                         & 1.0 & 1.038(32)& 1.743(17)& 0.123(16)\\

@@

            RNG          & 0.0 & 0.992(11)& 1.740(2) & 0.130(1) \\
                         & 0.1 & 0.987(12)& 1.746(5) & 0.133(4) \\
                         & 0.2 & 1.010(9) & 1.756(14)& 0.123(10)\\
                         & 0.5 & 1.010(16)& 1.750(16)& 0.143(13)\\
                         & 1.0 & 1.013(6) & 1.758(16)& 0.138(13)\\

@@

    are matching the expectations. Especially \(\nu\) and \(\gamma\)
    are always in very good agreement with their exact values. Because
    there can never be to much cross- and consistency checks, the ratio
    \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of

@@

    In fig. \ref{fig:Tc} \(T_c\) is plotted over \(\sigma\).

>>>>

\subsection{Finite Size Effects}
\label{ssec:finitesize}
    The aim of this thesis is to find the critical temperature \(T_c\)
    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean absolute magnetization \(\avg{|m|}\) of
    the system will show a steep decline to zero and the susceptibility
    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
    it is easy to see that the steep decline of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\) (here with a RNG).
    \begin{figure}[htbp]
        \centering
        \subfigure[Dependence of the Phase Transition on $\sigma$][]
        {
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        }
        \subfigure[Example for Finite Size Effects][]
        {
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        }
        \caption[Phase Transition and Finite Size Effects]
        {
            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying RNG with $L=128$.\\
            \subref{sfig:smeared_out:meanM}: Effects of different system
            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
        }
        \label{fig:smeared_out}
    \end{figure}\\
    But in the shown plots there occurs no steep decline to zero, but a
    smooth decline. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
    systems, hence no computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finte size effects}.
    These finite size effects cause a "smearing out" of the phase
    transition. This is stronger for smaller system sizes, as is visible
    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[S. ??]{NewmanBarkema1999}, which also yield the critical
    exponents. This will be performed in the next section.
    Though there is an easier approach, which yields comparable precise
    values for \(T_{c}\) in a much faster and more robust way, which is
    presented in \ref{ssec:binderIntersections}.

@@

    The determined values are displayed in tab. \ref{tab:critExp}.

@@

    and the error of \(T_c\) and \(\nu\) is the standard deviation of the
    three obtained values.\\

@@

        \begin{tabular}{l l l l l l}

@@

             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\

@@

            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & 2.2691... & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\

@@

            GG           & 0.0 & 2.2687(5)& 0.998(8) & 1.735(2) & 0.1262(4)\\
                         & 0.1 & 2.895(4) & 0.999(19)& 1.744(5) & 0.133(6) \\
                         & 0.3 & 2.527(1) & 1.029(30)& 1.724(16)& 0.129(12)\\
                         & 0.5 & 2.238(1) & 1.006(5) & 1.750(12)& 0.125(13)\\
                         & 1.0 & 2.128(2) & 1.038(32)& 1.743(17)& 0.123(16)\\

@@

            RNG          & 0.0 & 2.2689(7)& 0.992(11)& 1.740(2) & 0.130(1) \\
                         & 0.1 & 2.2058(8)& 0.987(12)& 1.746(5) & 0.133(4) \\
                         & 0.2 & 1.627(2) & 1.010(9) & 1.756(14)& 0.123(10)\\
                         & 0.5 & 1.2825(7)& 1.010(16)& 1.750(16)& 0.143(13)\\
                         & 1.0 & 1.2123(3)& 1.013(6) & 1.758(16)& 0.138(13)\\

@@

    are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
    agreement with the known value. Especially \(\nu\) and \(\gamma\)
    are always in very good agreement with their exact values. Besides the
    good agreement of the by data collapse obtained values of \(\nu\) and \(\gamma\),
    the ratio \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of

@@

    And in tab. \ref{tab:critTemp} the values are displayed together with the
    values obtained by the data collapse from the section before.
        \begin{tabular}{l @{\quad} l l @{\quad} l l}
             & \multicolumn{2}{c}{GG} & \multicolumn{2}{c}{RNG}\\
            \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)} & \multicolumn{1}{c}{\(T_c\)} & \multicolumn{1}{c}{\(T_c^{\mathrm{collapse}}\)}\\
            0.00 & 2.2689(2)& 2.2687(5) & 2.2690(2)& 2.2689(7)\\
            0.03 & 2.851(1) &           & 2.2679(4)&          \\
            0.05 & 2.863(1) &           & 2.2662(5)&          \\
            0.08 & 2.882(2) &           & 2.2548(6)&          \\
            0.10 & 2.893(2) & 2.895(4)  & 2.205(1) & 2.2058(8)\\
            0.12 & 2.903(3) &           & 2.1010(5)&          \\
            0.15 & 2.903(3) &           & 1.898(2) &          \\
            0.20 & 2.8274(6)&           & 1.624(1) & 1.627(2) \\
            0.25 & 2.676(2) &           & 1.4812(5)&          \\
            0.30 & 2.526(4) & 2.527(1)  & 1.407(2) &          \\
            0.40 & 2.332(4) &           & 1.327(4) &          \\
            0.50 & 2.233(7) & 2.238(1)  & 1.2818(2)& 1.2825(7)\\
            0.60 & 2.183(3) &           & 1.252(2) &          \\
            0.70 & 2.154(8) &           & 1.234(1) &          \\
            0.80 & 2.140(3) &           & 1.223(1) &          \\
            0.90 & 2.132(1) &           & 1.214(4) &          \\
            1.00 & 2.121(8) & 2.128(2)  & 1.208(5) & 1.2123(3)\\
            1.10 & 2.116(11)&           & 1.206(1) &          \\
            1.20 & 2.113(4) &           & 1.204(2) &          \\
        \caption{Critical temperatures for different $\sigma$}
        \label{tab:critTemp}
    The values obtained through the data collapse and the values obtained
    through the intersection of the binder cumulant are always in good
    agreement and of comparable precision.\\
    These values of \(T_c\) are plotted over \(\sigma\) in fig. \ref{fig:Tc}.
